### 2022-07-27 thesis/prelim.tex
Added appendix and some tikz figures

Examples of prominent non-linear dynamical systems include the Lotka-Volterra predator-prey model \cite{wangersky1978lotka}, the Fitz-Hugh Neuron model \cite{fitzhugh1961impulses}, and the recently introduced COVID19 disease model \cite{indiansuper2020supermodel}. Throughout this thesis, we discretize any continuous dynamics through the well-known Euler method. Thus, up to some error term of bounded degree, we can turn any non-linear system into the form given by Equation~\ref{eq:sys}.
%
\begin{example}
The SIR Epidemic model is a 3-dimensional dynamical system governed by the following continuous dynamics:
\begin{align} \label{eqn:sir}
    \begin{split}
        s' &= \beta \cdot s i \\
        i' &= \beta \cdot s i - \gamma \cdot i \\
        r' &= \gamma \cdot i
    \end{split}
\end{align}
where $s,i,r$ represent the fractions of a population of individuals designated as \textit{susceptible}, \textit{infected}, and \textit{recovered} respectively. There are two parameters, namely $\beta$ and $\gamma$, which influence the evolution of the system. $\beta$ is labeled as the \emph{contraction rate} and $1/\gamma$ is the \emph{mean infective period}.
%
Discretizing Equation~\ref{eqn:sir} according the Euler method yields the dynamics:

\begin{center}
\label{fig:discrete_sir}
  \begin{equation*}
      \begin{split}
          s_{k+1} &= s_k - (\beta \cdot s_k i_k)\cdot\Delta \\
          i_{k+1} &= i_k + (\beta \cdot s_k i_k - \gamma \cdot i_k)\cdot\Delta \\
          r_{k+1} &= r_k + (\gamma\cdot i_k)\cdot\Delta
      \end{split}
  \end{equation*}
  \captionof{figure}{Discretized Dynamics of SIR model}
\end{center}
 Here, $\Delta$ is the discretization step and the index $k \in \mathbb{N}$ simply represents the current step.
%For the benchmarks, we set $\beta = 0.34$, $\gamma=0.05$, and $\Delta=0.5$.
%
Note the non-linear terms $s_ki_k$ which preclude the expression of the dynamics as a linear transformation.
\end{example}

@@

\begin{definition}
\label{def:ptope}
A \emph{parallelotope} $P \subset \mathbb{R}^{n}$ is captured by the tuple $\langle \Lambda, c\rangle$ where $\Lambda \in \mathbb{R}^{2n \times n}$ is a matrix and $c \in \reals^{2n}$ is a column vector. We impose the condition that $\Lambda_{i+n} = -\Lambda_{i}$ for all $i \in \{1, \ldots, n\}$ such that
%
\begin{equation}
\label{eq:halfspace}
x \in P \mbox{ if and only if } \Lambda x \leq c.
\end{equation}
\end{definition}
%
We deem $\Lambda$ as the \emph{template direction matrix} where $\Lambda_i$ denotes the $i^{th}$ row of $\Lambda$ called the \emph{$i^{th}$ template direction}. The column vector $c$ is called the \emph{offset vector} with $c(i)$ denoting the $i^{th}$ element of $c$.
%
If we unpack Equation~\ref{eq:halfspace}, we can re-express the inequalities as a conjunction of half-space constraints. If we define $c_{u} = [c(1), c(2), \cdots, c(n)]^T$ and $c_{l} = [c(n+1), c(n+2), \cdots, c(2n)]^T$, then Equation~\ref{eq:halfspace} tells us that:
%
\begin{align}
  & \Lambda_i x \leq c_u(i)  \label{eq:upper_ineq}\\
  -& \Lambda_i x \leq c_l(i) \label{eq:lower_ineq}
\end{align}
%
Additionally, the definition of the paralleotope above requires that for each of $n$ ``positive" directions, there must exist a corresponding ``negative" direction. This is encoded into the template matrix $\Lambda$ by the condition $\Lambda_{i+n} = -\Lambda_{i}$. However, by the observation made above, we only need to keep the positive directions and divide our offset vector into equal components with the top half encoding the offsets for the positive directions and the bottom half encoding the offsets for the negative directions. The bottom half must be multiplied by a negative sign to account for Inequality \ref{eq:lower_ineq}.
%
Combining these remarks yields the half-space representation of parallelotope $P$.
%
\begin{definition}
\label{def:halfspace_def}
The \emph{half-space representation} of parallelotope $P$ is tuple  $\langle \Lambda, c_l, c_u \rangle$ where $\Lambda \in \mathbb{R}^{n \times n}$ and $c_l, c_u \in \reals^n$
such that
\begin{equation}
\label{eq:halfspaceconst}
P =\{x ~|~ c_l \leq \Lambda x \leq c_u\}
\end{equation}
\end{definition}
%
\noindent In particular, as a bounded intersection of pairs of parallel half-spaces, it is convex.
%
\begin{example}
\label{ex:simple_ptope}
Consider the 2D plane, namely $\reals^2$. We can construct a couple of simple examples of parallelotopes. First, if we define our parallelotope's template direction matrix to be the rows of the matrix:
%
\begin{equation}
  \Lambda = \begin{bmatrix} 1 & 0 \\ 0 & 1 \end{bmatrix}
\end{equation}
%
We see that our template directions will be the vectors $[1,0]^T, [0,1]^T$. Suppose now we set our upper and lower offsets to be:
%
\begin{equation}
  c_l = [1,1]^T, \quad c_u = [2,2]^T
\end{equation}
Then by Definition \ref{def:halfspace_def}, the half-space representation is given by:
\begin{equation}
\begin{bmatrix}
  1 \\ 1
\end{bmatrix} \leq \begin{bmatrix}
    1 & 0 \\ 0 & 1
  \end{bmatrix}\begin{bmatrix}
   x \\ y
  \end{bmatrix} \leq \begin{bmatrix}
    2 \\ 2
  \end{bmatrix}
\end{equation}
%
Accordingly, the bounded region in space will be the intersection of the following linear constraints:
%
\begin{align}
  \begin{split}
  1 \leq x \leq 2 \\
  1 \leq y \leq 2
  \end{split}
\end{align}
This is exactly the shifted unitbox $[1,2] \times [1,2]$. In fact, we can easily generalize this a general $n$-dimensional system by considering the template direction matrix $\Lambda = I_n$ where $I_n$ is the $n \times n$ identity matrix and two offset vectors $c_l, c_u$ of length $n$. This would yield the shifted $n$-dimensional unitbox:

\begin{equation}
[c_l(1), \;c_u(1)] \times [c_l(2),\; c_u(2)] \times \cdots \times [c_l(n), \; c_u(n)]
\end{equation}
%
It is worth noting that axis-aligned box on the 2D plane above would give the representation:
\begin{align}
  \Lambda = \begin{bmatrix}
            1 & 0 \\
            0 & 1 \\
            -1 & 0 \\
            0 & -1 \\
            \end{bmatrix} , \quad c = [2,2,-1,-1]^T
\end{align}
if we were to convert the half-space representation above into the form defined in Equation \ref{eq:halfspace}.
%
From here on out, we refer to parallelotopes defined by the $n$ axis-aligned directions as the \emph{axis-aligned} parallelotopes.
%
For a visual plot of above axis-aligned parallelotope, see Figure \ref{fig:axis_align_ptope}

\begin{figure}
  \centering
  \includegraphics{example-image-a}
  \caption{Plot of the axis-aligned parallelotope of Example \ref{ex:simple_ptope}.}
  \label{fig:axis_align_ptope}
\end{figure}

@@

\begin{example}
  \label{ex:simple_diag_ptope}
  We can also consider the axis-aligned directions rotated $45^\circ$ counter-clockwise. This would yield the two diagonal directions $[1,1]^T, [-1,1]^T$. Suppose we set the upper and lower offsets to be $c_u = [1,1]^T$ and $c_l = [-1,-1]^T$ respectively, then once again by Definition \ref{def:halfspace_def}:
  %
  \begin{equation}
  \begin{bmatrix}
    -1 \\ -1
  \end{bmatrix} \leq \begin{bmatrix}
      1 & 1 \\ -1 & 1
    \end{bmatrix}\begin{bmatrix}
     x \\ y
    \end{bmatrix} \leq \begin{bmatrix}
      2 \\ 2
    \end{bmatrix}
  \end{equation}
  %
  The bounded region in $\reals^2$ will be the conjunction of the linear inequalities:
  %
  \begin{align}
    \begin{split}
    -1 \leq x + y \leq 1 \\
    -1 \leq y - x \leq 1
    \end{split}
  \end{align}
  %
  In general, we define \emph{diagonal directions} are defined to be vectors created by adding and subtracting distinct pairs of unit axis-aligned vectors from each other. As a matter of convenience however, we refer to \emph{diagonal parallelotopes} as those defined by a combination of axis-aligned and diagonal directions. This definition will be useful when we consider parallelotopes defined by unconventional directions (i.e those template directions which are neither axis-aligned nor diagonal). To see a visual plot of the diagonal parallelotope, see Figure \ref{fig:diagonal_ptope}.

  \begin{figure}
    \centering
    \includegraphics{example-image-b}
    \caption{Plot of the rotated parallelotope of Example \ref{ex:simple_diag_ptope}.}
    \label{fig:diagonal_ptope}
  \end{figure}
\end{example}

\noindent Alternatively, a parallelotope can also be represented in a generator representation.
%
\begin{definition}
\label{def:generator_def}
The \emph{generator representation} of a parallelotope $P$ is a tuple of vectors $\langle v, g_1, \ldots, g_n\rangle$ such that $v,g_1, \cdots g_n \in \reals^n$. The vector  $v \in \mathbb{R}^n$ is called the \emph{anchor} and the $g_i \in \mathbb{R}^n$, are called the \emph{generators}. The parallelotope is defined as the set:
$$
P := \{ x ~|~ \exists \alpha_1, \ldots, \alpha_n \in [0,1], \; x = v + \sum_{i=1}^n \alpha_i g_i \}
$$
\end{definition}
%
\begin{remark}
  \noindent This is esstentially a convex reprsentation of the parallelotope, which shares many similarities to Zonotopes~\cite{girard2005reachability,althoff2010computing} and Star sets~\cite{duggirala2016parsimonious}.
  %
  In particular, a parallelotope is a special case of a zonotope where the number of generators is exactly the dimension of the system $n$.
\end{remark}
%
There is a simple method to convert from the half-space representation of $P$ to its equivalent generator representation. The algorithm is sketched in Algorithm \ref{alg:rep_conversion}.
%
The first line ascertains the lower-most vertex of the input parallelotope. This vertex will be our anchor. The first loop starting at line two finds all of the vertices which are incident to the lower-most vertex through an edge. Finally, the second loop starting at line eight calculates the generator vectors which will span the paralleltope through a convex combination $\bar{\alpha} \in [0,1]^n$. Note that the anchor is simply shifting the  generator vectors $g_i$ from the origin to the point required to properly span $P$.

@@

\begin{example}
Let us return to the axis-aligned box considered in Example \ref{ex:simple_ptope}.
%
To obtain the anchor, we end up with the trivial solution $x = 1, y=1$ by adhering to Step 1. Hence, the anchor is set to $v = (1,1)$
%
Subsequently, we solve for the two other vertices by following Step 2 to obtain $x=2, y= 1$ and $x=1,y=2$.
%
By Step 3, this would imply that the two generators are $g_1 = (2,1)-(1,1) = (1,0)$ and $g_2 = (1,2)-(1,1) = (0,1)$.
%
Now combine the anchor and generators to get the generator representation for this paralellotope:
%
\begin{equation}
 P = (1,1) + \alpha_1\cdot(1,0) + \alpha_2\cdot(0,1) \quad \alpha_1, \alpha_2 \in [0,1]
\end{equation}
%
This is exactly the unit box $[0,1]^2$ with its corner at the origin shifted to $(1,1)$.
\end{example}
%
\begin{example}
\label{ex:diag_ptope}
Once again, consider the space $\reals^2$ and the parallelotope $P$ given in half-plane representation as $0 \leq x-y \leq 1$, $0 \leq y \leq 1$.
%
This is a parallelotope with vertices at $(0,0)$, $(1,0)$, $(2,1)$, and $(1,1)$.
%
In the half-space representation, the template directions of the parallelotope $P$ are given by the directions $[1, -1]$ and $[0, 1]$.
%
The half-space representation in matrix form is given as follows:
%
\begin{equation}
  \begin{bmatrix} 0 \\ 0 \end{bmatrix} \leq \begin{bmatrix}  1 & -1 \\ 0 &  1 \end{bmatrix}  \begin{bmatrix} x \\ y \end{bmatrix} \leq \begin{bmatrix} 1 \\ 1 \end{bmatrix}. \label{eq:ptopeexample}
\end{equation}
%
To compute the generator representation of $P$, we need to compute the \emph{anchor} and the \emph{generators}.
%
The anchor is obtained by solving the linear equations $x-y = 0, y = 0$.
%
Therefore, the anchor $a$ is the vertex at origin $(0,0)$
%
To compute the two generators of the parallelotope, we compute two vertices of the parallelotope.
%
Vertex $v_1$ is obtained by solving the linear equations $x - y = 1, y = 0$.
%
Therefore, vertex $v_1$ is the vertex $(1,0)$.
%
Similarly, vertex $v_2$ is obtained by solving the linear equations $x-y = 0, y = 1$.
%
Therefore, $v_2$ is the vertex $(1,1)$.
%
The generator $g_1$ is the vector $v_1 - a$, that is $(1,0)- (0,0) = (1,0)$
%
The generator $g_2$ is the vector $v_2 - a$, that is $(1,1) - (0,0) = (1,1)$.
%
Therefore, all the points in the paralellotope can be written as $(x,y) = (0,0) + \alpha_1 \cdot (1,0) + \alpha_2\cdot (1,1)$, $\alpha_1, \alpha_2 \in [0,1]$.
\end{example}
%
%We denote this affine transformation as $T_{p}$.
%
\begin{definition}
A parallelotope bundle $Q$ is a set of parallelotopes $\{P_0, \ldots, P_m\}$ such that
  $$ Q = \bigcap_{i=1}^{m}P_i $$.
\end{definition}

>>>>

Examples of prominent non-linear dynamical systems include the Lotka-Volterra predator-prey model \cite{wangersky1978lotka}, the Fitz-Hugh Neuron model \cite{fitzhugh1961impulses}, and the recently introduced COVID19 disease model \cite{indiansuper2020supermodel}. Throughout this thesis, we discretize any continuous dynamics through the well-known Euler method. Thus, up to some error term of bounded degree, we can turn any non-linear system into the form given by Equation~\ref{eq:sys}.
%
\begin{example}
The SIR Epidemic model is a 3-dimensional dynamical system governed by the following continuous dynamics:
\begin{align} \label{eqn:sir}
    \begin{cases}
        s' &= \beta \cdot s i \\
        i' &= \beta \cdot s i - \gamma \cdot i \\
        r' &= \gamma \cdot i
    \end{cases}
\end{align}
where $s,i,r$ represent the fractions of a population of individuals designated as \textit{susceptible}, \textit{infected}, and \textit{recovered} respectively. There are two parameters, namely $\beta$ and $\gamma$, which influence the evolution of the system. $\beta$ is labeled as the \emph{contraction rate} and $1/\gamma$ is the \emph{mean infective period}.
%
Discretizing Equation~\ref{eqn:sir} according the Euler method yields the dynamics:

\begin{center}
\label{fig:discrete_sir}
  \begin{equation*}
      \begin{cases}
          s_{k+1} &= s_k - (\beta \cdot s_k i_k)\cdot\Delta \\
          i_{k+1} &= i_k + (\beta \cdot s_k i_k - \gamma \cdot i_k)\cdot\Delta \\
          r_{k+1} &= r_k + (\gamma\cdot i_k)\cdot\Delta
      \end{cases}
  \end{equation*}
  \captionof{figure}{Discretized Dynamics of SIR model}
\end{center}
 Here, $\Delta$ is the discretization step and the index $k \in \mathbb{N}$ simply represents the current step.
%For the benchmarks, we set $\beta = 0.34$, $\gamma=0.05$, and $\Delta=0.5$.
%
Note the non-linear terms $s_ki_k$ which preclude the expression of the dynamics as a linear transformation.
\end{example}

@@

\begin{definition}
\label{def:ptope}
A \emph{parallelotope} $P \subset \mathbb{R}^{n}$ is captured by the tuple $\langle \Lambda, c\rangle$ where $\Lambda \in \mathbb{R}^{2n \times n}$ is a matrix and $c \in \reals^{2n}$ is a column vector. We impose the condition that $\Lambda_{i+n} = -\Lambda_{i}$ for all $i \in \{1, \ldots, n\}$ such that
%
\begin{equation}
\label{eq:halfspace}
x \in P \mbox{ if and only if } \Lambda x \leq c.
\end{equation}
%
\end{definition}
%
We deem $\Lambda$ as the \emph{template direction matrix} where $\Lambda_i$ denotes the $i^{th}$ row of $\Lambda$ called the \emph{$i^{th}$ template direction}. The column vector $c$ is called the \emph{offset vector} with $c(i)$ denoting the $i^{th}$ element of $c$.
%
If we unpack Equation~\ref{eq:halfspace}, we can re-express the inequalities as a conjunction of half-space constraints. If we define $c_{u} = [c(1), c(2), \cdots, c(n)]^T$ and $c_{l} = [c(n+1), c(n+2), \cdots, c(2n)]^T$, then Equation~\ref{eq:halfspace} tells us that:
%
\begin{align}
  & \Lambda_i x \leq c_u(i)  \label{eq:upper_ineq}\\
  -& \Lambda_i x \leq c_l(i) \label{eq:lower_ineq}
\end{align}
%
Additionally, the definition of the paralleotope above requires that for each of $n$ ``positive" directions, there must exist a corresponding ``negative" direction. This is encoded into the template matrix $\Lambda$ by the condition $\Lambda_{i+n} = -\Lambda_{i}$. However, by the observation made above, we only need to keep the positive directions and divide our offset vector into equal components with the top half encoding the offsets for the positive directions and the bottom half encoding the offsets for the negative directions. The bottom half must be multiplied by a negative sign to account for Inequality \ref{eq:lower_ineq}.
%
Combining these remarks yields the half-space representation of parallelotope $P$.
%
\begin{definition}
\label{def:halfspace_def}
The \emph{half-space representation} of parallelotope $P$ is tuple  $\langle \Lambda, c_l, c_u \rangle$ where $\Lambda \in \mathbb{R}^{n \times n}$ and $c_l, c_u \in \reals^n$
such that
\begin{align}
\label{eq:halfspaceconst}
P & =\{x ~|~ c_l \leq \Lambda x \leq c_u\}
\intertext{In a more explicit form:}
P & = \bigwedge_{i=1}^n \left[c_l(i) \leq \Lambda_i\cdot x \leq c_u(i) \right]
\end{align}
\end{definition}
%
\noindent In particular, as a bounded intersection of pairs of parallel half-spaces, it is convex.
%
\begin{example}
\label{ex:simple_ptope}
Consider the 2D plane, namely $\reals^2$. We can construct a couple of simple examples of parallelotopes. First, if we define our parallelotope's template direction matrix to be the rows of the matrix:
%
\begin{equation}
  \Lambda = \begin{bmatrix} 1 & 0 \\ 0 & 1 \end{bmatrix}
\end{equation}
%
We see that our template directions will be the vectors $[1,0]^T, [0,1]^T$. Suppose now we set our upper and lower offsets to be:
%
\begin{equation}
  c_l = [-1,-1]^T, \quad c_u = [1,1]^T
\end{equation}
Then by Definition \ref{def:halfspace_def}, the half-space representation is given by:
\begin{equation}
\begin{bmatrix}
  -1 \\ -1
\end{bmatrix} \leq \begin{bmatrix}
    1 & 0 \\ 0 & 1
  \end{bmatrix}\begin{bmatrix}
   x \\ y
  \end{bmatrix} \leq \begin{bmatrix}
    1 \\ 1
  \end{bmatrix}
\end{equation}
%
Accordingly, the bounded region in space will be the intersection of the following linear constraints:
%
\begin{align}
  \begin{split}
  -1 \leq x \leq 1 \\
  -1 \leq y \leq 1
  \end{split}
\end{align}
This is exactly the shifted unitbox $[-1,1] \times [-1,1]$. In fact, we can easily generalize this a general $n$-dimensional system by considering the template direction matrix $\Lambda = I_n$ where $I_n$ is the $n \times n$ identity matrix and two offset vectors $c_l, c_u$ of length $n$. This would yield the shifted $n$-dimensional unitbox:

\begin{equation}
[c_l(1), \;c_u(1)] \times [c_l(2),\; c_u(2)] \times \cdots \times [c_l(n), \; c_u(n)]
\end{equation}
%
It is worth noting that axis-aligned box on the 2D plane above would give the representation:
\begin{align}
  \Lambda = \begin{bmatrix*}[r]
            1 & 0 \\
            0 & 1 \\
            -1 & 0 \\
            0 & -1 \\
            \end{bmatrix*} , \quad c = [2,2,-1,-1]^T
\end{align}
if we were to convert the half-space representation above into the form defined in Equation \ref{eq:halfspace}.
%
From here on out, we refer to parallelotopes defined by the $n$ axis-aligned directions as the \emph{axis-aligned} parallelotopes.
%
For a visual plot of above axis-aligned parallelotope, see Figure \ref{fig:axis_align_ptope}.

\begin{figure}[h!]
  \centering
  \begin{tikzpicture}
    \draw[step=1cm,gray,very thin, style=help lines] (-3,-3) grid (3,3);
    \fill[blue!40!white, opacity=0.4] (-1,-1) rectangle (1,1);
    \draw[->, thick](0,1) -- (0,2) node[above] (0,2) {$[0,1]$};
    \draw[->, thick](1,0) -- (2,0) node[right] (2,0) {$[1,0]$};
    \draw[->, thick](-1,0) -- (-2,0) node[left] (-2,0) {$[-1,0]$};
    \draw[->, thick](0,-1) -- (0,-2) node[below] (0,-2) {$[0,-1]$};
  \end{tikzpicture}
  \caption{Plot of the axis-aligned parallelotope of Example \ref{ex:simple_ptope}. The template directions are displayed as normal vectors to the pairs of parallel planes defining the parallelotope.}
  \label{fig:axis_align_ptope}
\end{figure}

@@

\begin{example}
  \label{ex:simple_diag_ptope}
  We can also consider the axis-aligned directions rotated $45^\circ$ counter-clockwise. This would yield the two diagonal directions $[1,1]^T, [-1,1]^T$. Suppose we set the upper and lower offsets to be $c_u = [1,1]^T$ and $c_l = [-1,-1]^T$ respectively, then once again by Definition \ref{def:halfspace_def}:
  %
  \begin{equation}
  \begin{bmatrix}
    -1 \\ -1
  \end{bmatrix} \leq \begin{bmatrix*}[r]
      1 & 1 \\ -1 & 1
    \end{bmatrix*}\begin{bmatrix}
     x \\ y
    \end{bmatrix} \leq \begin{bmatrix}
      1 \\ 1
    \end{bmatrix}
  \end{equation}
  %
  The bounded region in $\reals^2$ will be the conjunction of the linear inequalities:
  %
  \begin{align}
    \begin{split}
    -1 \leq x + y \leq 1 \\
    -1 \leq y - x \leq 1
    \end{split}
  \end{align}
  %
  In general, we define \emph{diagonal directions} are defined to be vectors created by adding and subtracting distinct pairs of unit axis-aligned vectors from each other. As a matter of convenience however, we refer to \emph{diagonal parallelotopes} as those defined by a combination of axis-aligned and diagonal directions. This definition will be useful when we consider parallelotopes defined by unconventional directions (i.e those template directions which are neither axis-aligned nor diagonal). To see a visual plot of the diagonal parallelotope, see Figure \ref{fig:diagonal_ptope}.

  \begin{figure}[h!]
    \centering
    \begin{tikzpicture}
      \draw[step=1cm,gray,very thin, style=help lines] (-3,-3) grid (3,3);
      \draw[fill=blue!40!white, opacity=0.4] (1,0) -- (0,1) -- (-1,0) -- (0,-1) -- cycle;
      \draw[->, thick] (0.5,0.5) -- (1,1) node[above] {$[1,1]$};
      \draw[->, thick] (-0.5,-0.5) -- (-1,-1) node[below] {$[-1,-1]$};
      \draw[->, thick] (-0.5,0.5) -- (-1,1) node[above] {$[-1,1]$};
      \draw[->, thick] (0.5,-0.5) -- (1,-1) node[below] {$[1,-1]$};

    \end{tikzpicture}
    \caption{Plot of the rotated parallelotope of Example \ref{ex:simple_diag_ptope}. Once again, note the manner in which the template directions and their negative counterparts define parallel planes and the parallelotope's definition as the intersection of the postive and negative half-spaces of all pairs of parallel planes.}
    \label{fig:diagonal_ptope}
  \end{figure}
\end{example}

\noindent Alternatively, a parallelotope can also be represented in a generator representation.
%
\begin{definition}
\label{def:generator_def}
The \emph{generator representation} of a parallelotope $P$ is a tuple of vectors $\langle v, g_1, \ldots, g_n\rangle$ such that $v,g_1, \cdots g_n \in \reals^n$. The vector  $v \in \mathbb{R}^n$ is called the \emph{anchor} and the $g_i \in \mathbb{R}^n$, are called the \emph{generators}. The parallelotope is defined as the set:
$$
P := \{ x ~|~ \exists \alpha_1, \ldots, \alpha_n \in [0,1], \; x = v + \sum_{i=1}^n \alpha_i g_i \}
$$
\end{definition}
%
\begin{remark}
  \noindent This is esstentially a convex reprsentation of the parallelotope, which shares many similarities to Zonotopes~\cite{girard2005reachability,althoff2010computing} and Star sets~\cite{duggirala2016parsimonious}.
  %
  %In particular, a parallelotope is a special case of a zonotope where the number of generators is exactly the dimension of the system $n$.
  %
  The most general definition of so-called \emph{template polyhedra} in $\reals^n$ is a tuple $\langle \Lambda, c \rangle$ such that $\Lambda \in \reals^{m \times n}$ for some $m \in \mathbb{N}$ and $c \in \reals^n$. The polyhedron is defined by the conjunction of linear
 inequalities:
%
 \begin{equation}
  \bigwedge_{i=1}^m \Lambda_i \cdot x \leq c_i
 \end{equation}
 %
It follows that parallelotopes are template polyhedra with $m=2n$ and the constraint that $\Lambda_{i+n} = -\Lambda_{i}$ for $1 \leq i \leq n$. Several verification tasks of hybrid automata have been investigated in the reachability literature. See \cite{dang2011template, gronski2019template, sankaranarayanan2008symbolic} for on related topics.
\end{remark}
%
There is a simple method to convert from the half-space representation of $P$ to its equivalent generator representation. The algorithm is sketched in Algorithm \ref{alg:rep_conversion}.
%
The first line ascertains the lower-most vertex of the input parallelotope. This vertex will be our anchor. The first loop starting at line two finds all of the vertices which are incident to the lower-most vertex through an edge. Finally, the second loop starting at line eight calculates the generator vectors which will span the paralleltope through a convex combination $\bar{\alpha} \in [0,1]^n$. Note that the anchor is simply shifting the  generator vectors $g_i$ from the origin to the point required to properly span $P$.

@@

\begin{example}
Let us return to the axis-aligned box considered in Example \ref{ex:simple_ptope}.
%
To obtain the anchor, we end up with the trivial solution $x = 1, y=1$ by adhering to Step 1. Hence, the anchor is set to $v = (1,1)$
%
Subsequently, we solve for the two other vertices by following Step 2 to obtain $x=2, y= 1$ and $x=1,y=2$.
%
By Step 3, this would imply that the two generators are $g_1 = (2,1)-(1,1) = (1,0)$ and $g_2 = (1,2)-(1,1) = (0,1)$.
%
Now combine the anchor and generators to get the generator representation for this paralellotope:
%
\begin{equation}
 P = (1,1) + \alpha_1\cdot(1,0) + \alpha_2\cdot(0,1) \quad \alpha_1, \alpha_2 \in [0,1]
\end{equation}
%
This is exactly the unit box $[0,1]^2$ with its corner at the origin shifted to $(1,1)$.
\end{example}
%
\begin{example}
\label{ex:diag_ptope}
Once again, consider the space $\reals^2$ and the parallelotope $P$ given in half-plane representation as $0 \leq x-y \leq 1$, $0 \leq y \leq 1$.
%
This is a parallelotope with vertices at $(0,0)$, $(1,0)$, $(2,1)$, and $(1,1)$.
%
In the half-space representation, the template directions of the parallelotope $P$ are given by the directions $[1, -1]$ and $[0, 1]$.
%
The half-space representation in matrix form is given as follows:
%
\begin{equation}
  \begin{bmatrix} 0 \\ 0 \end{bmatrix} \leq \begin{bmatrix*}[r]  1 & -1 \\ 0 &  1 \end{bmatrix*}  \begin{bmatrix} x \\ y \end{bmatrix} \leq \begin{bmatrix} 1 \\ 1 \end{bmatrix}. \label{eq:ptopeexample}
\end{equation}
%
To compute the generator representation of $P$, we need to compute the \emph{anchor} and the \emph{generators}.
%
The anchor is obtained by solving the linear equations $x-y = 0, y = 0$.
%
Therefore, the anchor $a$ is the vertex at origin $(0,0)$
%
To compute the two generators of the parallelotope, we compute two vertices of the parallelotope.
%
Vertex $v_1$ is obtained by solving the linear equations $x - y = 1, y = 0$.
%
Therefore, vertex $v_1$ is the vertex $(1,0)$.
%
Similarly, vertex $v_2$ is obtained by solving the linear equations $x-y = 0, y = 1$.
%
Therefore, $v_2$ is the vertex $(1,1)$.
%
The generator $g_1$ is the vector $v_1 - a$, that is $(1,0)- (0,0) = (1,0)$
%
The generator $g_2$ is the vector $v_2 - a$, that is $(1,1) - (0,0) = (1,1)$.
%
Therefore, all the points in the paralellotope can be written as $(x,y) = (0,0) + \alpha_1 \cdot (1,0) + \alpha_2\cdot (1,1)$, $\alpha_1, \alpha_2 \in [0,1]$.
\end{example}
%
%We denote this affine transformation as $T_{p}$.
%
\begin{definition}
A parallelotope bundle $Q$ is a set of parallelotopes $\{P_0, \ldots, P_m\}$ such that
  $$ Q = \bigcap_{i=1}^{m}P_i $$.
\end{definition}
